# Tables {sec-tables}

```{r}
#| label: setup-tables
library(dplyr, warn.conflicts = FALSE)
```


I did a lot of experimenting with tables when creating the [L2C Master Descriptive Table website](https://brad-cannell.github.io/l2c_master_table/). I need to add notes on creating and working with tables in this chapter. I may also want to add it to the [appendix in R4Epi](https://www.r4epi.com/appendix-alternative-table-formats. 

Useful websites:

- [Quarto table documentation](https://quarto.org/docs/authoring/tables.htm)


## Test table

Just quickly testing to see if it will download. Need to better document this in the future.

```{r}
#| label: demographics-variable-name-key

key <- tribble(
 ~var, ~description,
 "ml_age", "Participant's age at baseline.",
 "ml_gender_f", "Participant's self-reported sex at baseline.",
 "ml_race_f", "Participant's self-reported race at baseline.",
 "ml_race_eth_4cat_f", "Participant's self-reported race at baseline. Collapsed into four categories.",
 "ml_hispanic_f", "Participant's self-report of Hispanic ethnicity at baseline."
)

```

Initially, the code chunk above created a datatable version of the table. 

````
```{{r}}
DT::datatable(
  key,
  colnames = c("Variable Name", "Variable Description")
)
```
````

When I tried to render the book, I got the following error:

````
Error: Functions that produce HTML output found in document targeting pdf output.
Please change the output type of this document to HTML. Alternatively, you can allow
HTML output in non-HTML formats by adding this option to the YAML front-matter of
your quarto file:

  prefer-html: true

Note however that the HTML output will not be visible in non-HTML formats.

Execution halted
````

```{r}
knitr::kable(key)
```

## Issues

- Why do I get `?@tbl-demographics-overall` and how do I fix it?
  - There may be other reasons why this error can occur, but I was getting it because [Quarto doesn't currently support table captions for datatables](https://github.com/quarto-dev/quarto-cli/discussions/3034). You can, however, use figure captions for datatables.